{ \fontfamily{ptm}\selectfont Error Bound Can Give Near Optimal Convergence Rate for Inexact Accelerated Proximal Gradient Method }

### 2025-10-16 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, fixes

            The assumption is about $(f, g, L)$. 

@@

                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz function. 

@@

@@

        \begin{assumption}[for inexact proximal operator]\;\label{ass:for-inxt-prox}\\

@@

    \begin{assumption}[error bound for proximal problem]\;\label{ass:eb-for-pp}\\
        This assumption is about $(g, \omega, A, \Psi_\lambda, \gamma_\lambda)$
            \item Assume function $\Psi_\lambda$ as given by \eqref{eqn:dual-pp} which satisfies gradient mapping error bound (Assumption \ref{ass:pg-eb}) where, $f(v) = \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) = \omega^\star(v)$. 
            \item Assume the primal objective $\Phi_\lambda$ is a $L_1$ Lipschitz continuous on its domain. 
            \item Assume $(f, g, L)$ satisfies Assumption \ref{ass:for-inxt-prox}, with $\gamma = \gamma_\lambda$ we can do this because $f$ is quadratic and has a Lipschitz continuous gradient. 
    \subsection{Error bound and linear convergence}

@@

            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:eb-for-pp} $\exists \gamma > 0$ such that: 

@@

        We can immediately claim quadratic growth condition when $\omega = \Vert \cdot\Vert_1$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:eb-for-pp} is true, and it's a case widely available in applications. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:eb-for-pp} also. 
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 

@@

            Consider the following proximal problem: 
                \item The primal proximal problem $\Phi_\lambda(u) = \frac{1}{2\lambda}\Vert u - y\Vert^2 + \omega(Au)$.
                \item The dual proximal problem $\Psi_\lambda(v) = f(v) + g(v)$ where \\ $f(v) := \frac{1}{2\lambda}\left\Vert \lambda A^\top v - y\right\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$. 
            If, $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 
            Let $L_1$ be the global Lipschitz continuity constant of $\Phi_\lambda$ which it has in this case. 
            Let $\tau \ge L, \epsilon \ge 0$, $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and let the iterates $(v_n)_{n \ge 0}$ be generated by it. 
            Then, there exists a minimizer $\bar v$ for $\Psi_\lambda$, and the followings are true: 

@@

                \item If we choose $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap satisfies for all $n \ge 0$ the inequality 
                $$\mathbf G_\lambda(z_n, v_n) \le \left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\left(1 + L_1\sqrt{2 \lambda}\right)(\Psi_\lambda(v_0) - \Psi_\lambda(\bar v)).$$
                \label{prop:inn-looplin-cnvg-item3}

@@

            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Proposition \ref{prop:1nrm-prox-problem} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:eb-for-pp}. 

@@

            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, it provides $\Phi_\lambda(z_n) - \Phi_\lambda(v_0)$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives: 
                \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_1 \sqrt{2\lambda}\left(

@@

                L_1\sqrt{2\lambda} \left(

@@

            At (1), we used convergence results from Theorem \ref{thm:lin-cnvg-ista-eb}. 

@@

                \mathbf G_\lambda(z_n, v_n) 
                &\underset{(?)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0

@@

                L_1 \sqrt{2\lambda}\left(

@@

@@

            To choose a feasible $v_0$, we can...
            \todoinline{
                REMEMBER TO FINISH IT. 

>>>>

            The assumption is about $(F, f, g, L)$. 

@@

                \item $f: \RR^n \rightarrow \RR$ is a convex, $L$ Lipschitz smooth function (i.e: $\nabla f$ is $L$ a Lipschitz continuous mapping). 

@@

                \item The over all objective is $F = f + g$. 

@@

        \begin{assumption}[linear composite of convex nonsmooth function]\;\label{ass:for-inxt-prox}\\

@@

    \subsection{Error bound and linear convergence of ISTA}

@@

            Now, for all $z = \bar x \in S$, from Assumption \ref{ass:lin-cnvg-for-pp} $\exists \gamma > 0$ such that: 

@@

        The following assumption characterizes a set of sufficient conditions of the proximal problem such that linear convergence rate of applying ISTA to dual proximal objective $\Psi_\lambda$ can be achieved. 
        \begin{assumption}[conditions for linear convergence of proximal problem]\;\label{ass:lin-cnvg-for-pp}\\
            This assumption is about $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$. 
                \item Assume $(g, \omega, A)$ satisfies Assumption \ref{ass:for-inxt-prox}. The primal objective $\Phi_\lambda$ is given by \eqref{eqn:primal-pp}, and dual $\Psi_\lambda$ by \eqref{eqn:dual-pp}. This means if we let $f(v) := \frac{1}{2\lambda}\Vert \lambda A^\top v - y\Vert^2 - \frac{1}{2\lambda}\Vert y\Vert^2, g(v) := \omega^\star(v)$, then $\Psi_\lambda = f + g$. 
                \item Next, assume $\Psi_\lambda = f + g$ satisfies Assumption \ref{ass:pg-eb} by viewing $\Psi_\lambda = F$ and denote $\gamma_\lambda := \gamma$. Note that we can do this because $f$ is obviously Lipschitz smooth. 
                \item Assume the primal objective $\Phi_\lambda$ is $L_\Phi^\lambda$ Lipschitz continuous. 
        The following propositions precisely show that the linear convergence is achievable when Assumption \ref{ass:lin-cnvg-for-pp} holds. 

@@

            Let the parameters $(g, \omega, A, \Phi_\lambda, \Psi_\lambda, L^\lambda_{\Phi} ,\gamma_\lambda)$ of a proximal problem satisfy Assumption \ref{ass:lin-cnvg-for-pp}. 
            Let $\tau \ge L_\Psi^\lambda$, and let $v_0 \in \dom \Psi_\lambda$ be an initial condition for an algorithm that satisfies Definition \ref{def:ista} with $F(v) = f(v) + g(v)$ and suppose that it generates iterates $(v_n)_{n \ge 0}$. 
            Let $\bar v$ be a minimizer of $\Psi_\lambda$, then the followings are true for all $\epsilon \ge 0$: 

@@

                \item If we let $z_n := y - \lambda A^\top v_n$, and $\bar z := y - \lambda A^\top \bar v$, then $\Phi_\lambda(z_n) - \Phi_\lambda(\bar z)$ converges linearly. \label{prop:inn-looplin-cnvg-item2}
                \item The duality gap has convergence $\mathbf G_\lambda(z_n, v_n) \le \mathcal O\left(\left(1 - \frac{\gamma_\lambda}{2\tau}\right)^{n/2}\right)$. \label{prop:inn-looplin-cnvg-item3}

@@

            To see \ref{prop:inn-looplin-cnvg-item1}, the sequence $\Psi_\lambda(v_n) - \Psi_\lambda(\bar v)$ has linear convergence by Theorem \ref{thm:lin-cnvg-ista-eb} because we assumed that $\Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 

@@

            Because the iterates are given by $z_n = y - \lambda A^\top v_n$, and $\bar z = y - \lambda A^\top \bar v$, due assumed Lipschitz continuity of $\Phi_\lambda$, we can use Theorem \ref{fact:minimizing-dual-pp} which gives: 
            \begin{align}\label{ineq:inn-loop-lin-cnvg-pitem2}
                \begin{split}
                    \Phi_\lambda(z_n) - \Phi_\lambda(\bar z) &\le L_\Phi^\lambda \sqrt{2\lambda}\left(

@@

                    L_\Phi^\lambda\sqrt{2\lambda} \left(

@@

                \end{split}
            At (1), we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}.

@@

                & \mathbf G_\lambda(z_n, v_n) 
                &\underset{(1)}{=} \Phi_\lambda(z_n) + \Psi_\lambda(v_n) + 0

@@

                L_\Phi^\lambda \sqrt{2\lambda}\left(

@@

                    L_\Phi^\lambda \sqrt{2\lambda}\left(
                    + 
                    \right)^{n/2} (\Psi_\lambda(v_0) - \Psi_\lambda(\bar v))
            At (1) we used strong duality because constraint qualification is in Assumption \ref{ass:for-inxt-prox}. 
            At (2) we used \eqref{ineq:inn-loop-lin-cnvg-pitem1}, \eqref{ineq:inn-loop-lin-cnvg-pitem2}. 
            To see \ref{prop:inn-looplin-cnvg-item4}, apply Theorem \ref{thm:dlty-gap-inxt-pp}. 

@@

            In pratice, use the proximal operator of $\omega^\star$ choose a feasible $v_0$. 
        The next proposition will characterize a precise case where Assumption \ref{ass:lin-cnvg-for-pp} is true, and it's a case widely available in applications. 
            In addition, if $g := \Vert \cdot\Vert_1$, then the function $\Psi_\lambda, \Psi_\lambda$ satisfies Assumption \ref{ass:lin-cnvg-for-pp}. 
            Therefore, $\Psi_\lambda$ is quasi-strongly convex then by \cite[Theorem 4]{necoara_linear_2019}, and \cite[Theorem 7]{necoara_linear_2019}, it satisfies error bound condition as given in Assumption \ref{ass:pg-eb}, hence Assumption \ref{ass:lin-cnvg-for-pp} also. 
